---
title: "lab_report_knapsack"
author: "Zuxiang Li, Ying Luo"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{lab_report_knapsack}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup}
library(assignment6Package)
library(lineprof)
```

```{r}
suppressWarnings(RNGversion("3.5.9"))
set.seed(42)
n <- 2000
knapsack_objects <- data.frame(
  w=sample(1:4000, size = n, replace = TRUE),
  v=runif(n = n, 0, 10000)
  )
```

# The knapsack package
The package will contain three diﬀerent functions for solving what is called the knapsack problem. The knapsack problem is a discrete optimization problem where we have a knapsack that can take a limited weight W and we want to ﬁll this knapsack with a number of items i = 1,...,n, each with a weight wi and a value vi. The goal is to ﬁnd the knapsack with the largest value of the elements added to the knapsack.

## Brute force search
Brute-force search giveS a correct answer in all situations for the knapsack problem.

Function knapsack_brute_force(x, W) that takes a data.frame cx with two variables v and w and returns the maximum knapsack value and which elements (rows in the data.frame). The variable W is the knapsack size.

If the parameter parallel is TRUE, the function would parallelize over the detected cores.

```{r}
brute_force_knapsack(x = knapsack_objects[1:8,], W = 3500)
brute_force_knapsack(x = knapsack_objects[1:12,], W = 3500)
brute_force_knapsack(x = knapsack_objects[1:8,], W = 2000)
brute_force_knapsack(x = knapsack_objects[1:12,], W = 2000)
```

## Dynamic programming
Implement Dynamic programming as knapsack_dynamic(x, W). This function would return the same results as the brute force algorithm, but much better since the algorithm will run in O(Wn).

```{r}
knapsack_dynamic(x = knapsack_objects[1:8,], W = 3500)
knapsack_dynamic(x = knapsack_objects[1:12,], W = 3500)
knapsack_dynamic(x = knapsack_objects[1:8,], W = 2000)
knapsack_dynamic(x = knapsack_objects[1:12,], W = 2000)
```

## Greedy heuristic
Using the a heuristic or approximation for the problem which will not give an exact result (but it can be shown that it will return at least 50% of the true maximum value), but it will reduce the computational complexity considerably (actually to O(nlogn) due to the sorting part of the algorithm).

```{r}
greedy_knapsack(x = knapsack_objects[1:800,], W = 3500)
greedy_knapsack(x = knapsack_objects[1:1200,], W = 2000)
```

## Profile your code and optimize your code
Using package lineprof to observe the time and alloc consumed in the function, identify bottlenecks.
```{r}
source("../R/knapsack.R")
l1<-lineprof(brute_force_knapsack(x = knapsack_objects[1:8,], W = 3500))
l1
l2<- lineprof(knapsack_dynamic(x = knapsack_objects[1:8,], W = 3500))
l2
l3<-lineprof(greedy_knapsack(x = knapsack_objects[1:800,], W = 3500))
l3
```


